A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-03-22 lctes18-reviews-11-rebuttal.txt

We would like to thank the reviewers for the thoughtful comments, questions,
and criticism.

In a final version, we will address the main concern among reviews regarding
the paper motivations.
We will discuss why having a formal semantics of the language is important, and
how it affected our own implementation.
We will also discuss why the main results of the paper (memory boundedness,
determinism, and termination) are particularly important in the context of
embedded systems.

We will also accommodate all requested clarifications and corrections (e.g.,
more intuitive/complete descriptions of the semantics, compare with some
specific work, etc.).
Some of the comments are also addressed individually as follows.

### 2018-04-10 07-artifact.tex
Ajustes no Artifact evaluation

\appendix
\section{Artifact appendix}

@@

{\em Obligatory. Use just a few informal keywords in all fields applicable to your artifacts
and remove the rest. This information is needed to find appropriate reviewers and gradually 
unify artifact meta information in Digital Libraries.}

{\small
\begin{itemize}
  %\item {\bf Algorithm: }
  %\item {\bf Program: }
  \item {\bf Compilation: } The output of the \CEU compiler is a C program that requires a C compiler (e.g., GCC-7.2).
  \item {\bf Transformations: } The compiler of \CEU is a Lua program (Lua-5.3) that generates a C program.
  %\item {\bf Binary: }
  \item {\bf Data set: } The data set is a set of program test cases included in the language distribution.
  \item {\bf Run-time environment: } Linux with Lua-5.3 and GCC-7.2. Root access is not required.
  \item {\bf Hardware: } Off-the-shelf Intel machine.
  %\item {\bf Run-time state: }
  \item {\bf Execution: } 5-10 minutes for the full test.
  \item {\bf Output: } Console output: Success (termination) or Fail (abortion).
  \item {\bf Experiments: } Manual steps by user.
  %\item {\bf Workflow frameworks used?: }
  %\item {\bf Publicly available?: } Yes: \url{https://github.com/fsantanna/ceu}
\end{itemize}

@@

Off-the-shelf Intel machine.

>>>>

\section{Artifact appendix}

@@

{\small
\begin{itemize}
  %\item {\bf Algorithm: }
  %\item {\bf Program: }
  \item {\bf Compilation: } The output of the \CEU compiler is a C program that requires a C compiler (e.g., GCC-7.2).
  \item {\bf Transformations: } The compiler of \CEU is a Lua program (Lua-5.3) that generates a C program.
  %\item {\bf Binary: }
  \item {\bf Data set: } The data set is a set of program test cases included in the language distribution.
  \item {\bf Run-time environment: } Linux with Lua-5.3 and GCC-7.2. Root access is required to install a single executable file.
  \item {\bf Hardware: } An off-the-shelf Intel machine.
  %\item {\bf Run-time state: }
  \item {\bf Execution: } 5-10 minutes for the full test.
  \item {\bf Output: } Console output: Success (termination) or Fail (abortion).
  \item {\bf Experiments: } Manual steps performed by the user in the command line.
  %\item {\bf Workflow frameworks used?: }
  %\item {\bf Publicly available?: } Yes: \url{https://github.com/fsantanna/ceu}
\end{itemize}

@@

An off-the-shelf Intel machine.
